\documentclass[11pt]{article}

\usepackage{mathtext}         % если нужны русские буквы в формулах (не обязательно)
\usepackage[T2A]{fontenc}     % внутренняя T2A кодировка TeX
\usepackage[russian]{babel}   % включение переносов
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\pagestyle{empty} % нумерация выкл.
\addtolength{\textheight}{1.75in}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{color}
\usepackage{setspace}
\definecolor{gray}{rgb}{0.4,0.4,0.4}

\newif\ifdetailed

\newif\ifproduct

% для полной версии резюме — detailedtrue, для сокращенной — detailedfalse
\detailedtrue
%\detailedfalse
\productfalse

\newif\iftwopage
\twopagetrue


\ifdetailed
%в полной версии много букв, поэтому поплотнее
\setstretch{0.8}
\fi

\begin{document}

\noindent {\sffamily{\Huge{\textbf{   Rauf Aliev   }}}}%
\ifdetailed
{\small{// {\textbf{DETAILED VERSION OF CV}}. {\color{gray} COMPACT VERSION IS HERE: \href{http://RaufAliev.ru/cv/eng}{RaufAliev/cv/eng/}}}}
\else
{\small{// {\textbf{SHORT VERSION OF CV}}. {\color{gray} FULL VERSION IS HERE: \href{http://RaufAliev.ru/cv/eng/full/}{RaufAliev/cv/eng/full/}}}}
\fi

\vspace{0.5em}

\noindent +7 906 710 56 10    |    \url{http://www.RaufAliev.ru}   |   \href{mailto:r.aliev@gmail.com}{r.aliev@gmail.com}  |  Moscow, Russia  \ifdetailed | Jan 2, 1978 \fi

\vspace{0.5em}

\hrule

\vspace{1.5em}

\ifdetailed
\noindent {\textbf{CAREER OBJECTIVE}}: To work in a dynamic/established company in IT related role (IT director, CTO, IT{}manager, project manager, solution architect, development manager, or functional/technical/pre-sales consultant) on consulting, development, or operations. Preferably working in Web, e-commerce, retail, but open to other industry, challenge and opportunities.
\else
\noindent {\textbf{Career objective}}: CTO, head of IT, head of web development, product director
\fi

\vspace{1em}

\ifdetailed
\noindent {\textbf{QUALIFICATIONS SUMMARY:}}
\begin{itemize}
\ifproduct
\else
\item Have 22 years of experience in IT industry, software development, and complex systems integration using various technologies (PHP, Perl, Delphi, C++, MySQL, HTML, Javascript)
\item Have 12 years of managerial experience as project leader, technical/IT manager, and project manager.
\item Have 4 years of experience in retail, e-commerce;
\item Excellent end-to-end functional knowledge in e-commerce, software development, DTP.
\item Have done PMI Project Management Professional (PMP) training (\href{http://pmexpert.ru/}{PM EXPERT}).
\item Have excellent skills in IT project management, business processes, pre-sales, development, documentation, testing, and training.
\item Have excellent skills in systems integration, data migration, business intelligence/reporting, analysis, design, and software development. Current technical skills are in Internet technologies, security, e-commerce.
\item Have excellent analytical/problem-solving skills, self-initiative and fast to learn new skills/technologies, resourceful, committed, and smart-worker.
\item Able to coordinate and communicate with project team. Able to work independently and part of team.
\item Able to communicate in Russian (native), English (upper intermediate) and French (basic).
\fi
\end{itemize}
\else
\noindent {\textbf{Profiles}}: 12 years of relevant experience (CTO, Head of IT etc.); Web, e-commerce {\em{(e.g.: Enter, Svyaznoy, Chronopay, NaDiske.ru);}}  focusing for Web/Internet during last 13 years,  Windows/Linux development, iOS/Android projects {\em (e.g. my own game \href{http://wordrive.com}{Wordrive})}, ERP/1C projects {\em (in Mail.Ru Group and ENTER)}, speaker (\href{http://2013.russianinternetforum.ru/p/details.php?ID=1129}{RIF}, \href{http://2012.russianinternetweek.ru/program/internet-management/}{RIW}, Codefest,{}…), IT consultant (RIK); quite good in technologies and methods:  Perl, PHP, Bash, SQL, Dephi, LaTeX, 1C, VBA, Office, PMI PMBOK, ITIL, AGILE. Education: Computer and networks, master degree, \href{http://www.rsreu.ru/index.php?lang=en}{Radio-Engineering University of Ryazan,}, \href{http://www.itexpert.ru/}{IT EXPERT}/\href{http://pmexpert.ru/}{PM EXPERT}.
\fi
\vspace{1em}

\ifdetailed
\noindent {\textbf{EMPLOYMENT HISTORY:}}
\fi

\begin{longtable} {l | p{0.85\textwidth}}

2013 — now & {\textbf{"\href{http://enter.ru}{ENTER}"}}{\small{\it{}}}\\
\ifdetailed
& {\textbf{Head of development department}} {\color{gray}\small{// Reporting to IT Director}}
\begin{itemize}
\item Arranged and managed key projects in areas such as Website development and ERP (1S) integration.
\item Developing and managing an annual IT budget
\item A broad range of employee supervision and development functions for 27-member staff, including making work schedules, tracking work time, and staff training;
\item Actively assist in all management operations for web e-commerce;
\end{itemize}
\\
\vspace{1em} & ENTER is a  federal nonfood retail chain. New retail format for Russia which combines Internet trading sites and traditional shops. Currently Enter has more than 70 offline shops. \\
\fi

\ifdetailed
\else
& {\textbf{Head of development department}}  \\
\vspace{1em} & {\it{HR management (30  employees), project management (10-15 projects), procurement management (4-6), implementing business processes in Web, QT, 1C. }} \\
\fi




2011 — 2013 & {\textbf{"\href{http://corp.mail.ru}{MAIL.RU GROUP}"}}\\

\ifdetailed
& {\textbf{Director of Research \& Education}} {\color{gray}\small{// Reporting to CEO}}
\begin{itemize}
\item Was responsible for a number of marketing and educational projects:
\item Teсhnораrk@Mаil.Ru (\url{http://tp.mail.ru}). it is designed to select and train students who will in future get jobs in Mail.ru Group structures. It has 22 teachers and 120 students.
\item the largest East European Programming Contest, Russiаn Cоde Cuр (3000+ participants,200+ guests, public talks and interviews broadcasted online)
\item the largest free-to-attend IT conference TechForum Mail.Ru 2012 Spring (1000+ participants, 20+ talks)
\end{itemize}
\\
\vspace{1em} & Mail.Ru Group is the largest internet company in Russian-speaking world and the leading Internet company based on global monthly unique users, \url{http://corp.mail.ru} \\
\newpage
\fi

\ifdetailed
\else
& {\textbf{Director of Research \& Education}} \\
\vspace{1em} & {\it{HR management (30  employees), project management (10-15 projects), procurement management (4-6), implementing business processes in Web, QT, 1C. }} \\

\fi


2010 — 2011 & {\textbf{"\href{http://chronopay.com}{CHRONOPAY}"}}\\


\ifdetailed
& {\textbf{Director of R\&D}} {\color{gray}\small{// Reporting to CEO}}
\begin{itemize}
\item Performed PCI-DSS security assessments in accordance with the PCI security
standard and local laws,
\item Carried out PCI DSS Level I formal assessments in SRC GmbH (documents,
negotiations with the auditor etc.).
\item A major integration project was successfully completed( the ChronoPayTransaero-Sabre GDS),
harmonized the processing software development and technical support system,
\iftwopage
\else
\item organized the development and launch of the new web-site.
\fi
\end{itemize}
\\
\vspace{1em} & Chronopay was one of the leading Payment Service Providers on the European Market, HQ-ed in Amsterdam, \url{http://chronopay.com} \\
\fi

\ifdetailed
\else
& {\textbf{Director of R\&D}} \\
\vspace{1em} & {\it{HR management (30  employees), project management, performed PCI-DSS security assessments. The largest project is Transaro-Sabre gateway. Chronopay was the largest VISA/Mastercard payment processing company in Russia till 2010}}. \\
\fi




2009 — 2010 & {\textbf{"\href{http://svyaznoy.ru}{SVYAZNOY}"}}\\

\ifdetailed
& {\textbf{CTO, e-commerce}} {\color{gray}\small{// Reporting to Director for direct sales}}
\begin{itemize}
\iftwopage
\else
\item Reporting to director for direct sales;
\item my role was system architect role with product manager
\fi
\item By 2010, I built a scalable and reliable solution that “survived” without any problems after
100,000 hosts before NY (GA), 160,000 in spring of 2010. Previously, the site could hardly maintain 40,000 hosts.
\item recruited, trained and managed a team of highly qualified experts (2-8 persons)
\item completed a project of geographically distributed federal e-commerce system of
\item 200 standalone terminals in a two-month period, within the commitment plans and
budgets, and with a small team of 2 specialists; and in three months from the
beginning of development – a new system was successfully released and
launched,
\item automated the billing system: price-lists from e-mail are published at the site
automatically,
\item implemented a task management system and version control system
\item developed and introduced SLA for the Department
\item launched electronic payments (Yandex.Money, VISA/Mastercard, RES.
WebMoney)
\item worked out CRM, BI projects.
\end{itemize}
\\
\vspace{1.5em} & Svyaznoy is Russia’s second largest independent handset retailer, 3000 stores \\
\fi

\ifdetailed
\else
& {\textbf{CTO, e-commerce}} \\
\vspace{1em} &  {\it{HR management (10 employees),  designed and prototyped new features, projects. Kiosks were designed, developed and launched less than 3 months for more that 100 locations. The development processes were optimized or created (JIRA, SLA, CVS).
}} \\
\fi

2008 — 2009 & {\textbf{"\href{http://webmediagroup.ru}{WEB MEDIA GROUP}"}}\\

\ifdetailed
& {\textbf{CTO}}  {\color{gray}\small{// Reporting to CEO}}
\begin{itemize}
\item 6 companies of the holding, 10 web sites, more than 20
servers, over 100 employees.
\item successfully prepared and implemented a hosting cost optimization project for the
company's servers - saved over 40\% of the monthly budget;
\item actively participated in selecting contractors, quality assurance, Dostavka.ru acquisition and launch (technical
part);
\item developed technical specifications and terms of reference;
\end{itemize}
\\
\vspace{1em} & Web Media Group is 20th of russian internet companies rating (\href{http://www.forbes.ru/investitsii-slideshow/nedvizhimost/79474-30/slide/20}{Forbes}) \\
\fi

\ifdetailed
\newpage
\else
& {\textbf{CTO}} \\
\vspace{1em} &  {\it{Regularly audited all the projects of the group (photosight.ru, bank.ru, dostavka.ru). Successfully prepared and implemented a hosting cost optimization project for the company’s servers - saved over 40 completed a load testing project; actively participated in the project of Dostavka.ru acquisition and launch;
}} \\
\fi

2004 — 2008 & {\textbf{"\href{http://rbcsoft.ru}{RBC SOFT (ARMADA)}"}}\\

\ifdetailed
& {\textbf{Head of project management department}} {\color{gray}\small{// Reporting to Director of Internet department}}
\begin{itemize}
\item Done the best to ensure the effective work of the department and project managers, hired
and trained the staff, carried out the regular quality audit, participated in key negotiations
and conducted presale presentations, designed the presale
management system.
\item  completed more than 100 IT projects per year for large
government and commercial customers in the total amount of \$ 2 million per year.
\item more than 50 projects were of my responsibility (Euroset’, Ingosstrakh, FGC UES, SU-155, Perekrestok, Rarebooks.ru, Republica,
PROTEK, Slavinvestbank, Russia IC, etc.), the total cost of all projects is over \$2.5mln
\end{itemize}
\\
\vspace{1em} & RBC SOFT is the second largest Internet developer as of 2008, \url{http://rbcsoft.ru} \\
\fi

\ifdetailed
\else
& {\textbf{Head of project management department}} \\
\vspace{1em} &  {\it{HR management (12+), quality management, negotiations, presentations, presale, 100 IT projects per year, more than 50 projects were of my responsibility (Euroset, Ingosstrakh, FSK EES, SU-155, Perekrestok, Protek,SK Rossia и др.)
}} \\
\fi

2001 — 2004 & {\textbf{"\href{http://artstyle.ru}{ARTSTYLE GROUP}"}}\\

\ifdetailed
& {\textbf{Head of IT}} {\color{gray}\small{// Reporting to CEO}}
\begin{itemize}
\item organized development of own cross-platform
programming language, Art Publishing (\url{http://ap.artstyle.net/}, C++/Unix/Windows),
designed specifically for rapid web development,
\item organized the development of CMS
ContentRIGHT - the control system completely based on Art Publishing + MySQL;
\item StarChat.ru - internet conferencing engine
\end{itemize}
\\
\fi

\ifdetailed
\else
& {\textbf{Head of IT}} \\
\vspace{1em} &  {\it{HR management (4+), projects - my own programming language, CMS ContentRIGHT, Starchat.ru internet conferencing engine and more than 30 websites.
}} \\
\fi

\end{longtable}

\ifdetailed
\noindent {\textbf{EDUCATION:}}
\begin{longtable} {l|p{0.5\textwidth}|l|l}
1994 — 1999   & Ryazan State Radio Engineering Academy (University), \url{http://www.rsrea.ru}        & Computers and Internet        & Master degree\\
2001 — 2003   & Moscow State Open Pedagogical University, http://www.msopu.ru & Pedagogics    & 2y, n/finished\\
2012    & Public Speaking Course        & Samolov and Samolova  & Certificate\\
2009    & Conversational English Course, upper Intermediate     & Buziness Class&       —\\
2008    & General English Course, Upper Intermediate    & Buziness Class&       —\\
2007    & General English, Intermediate 3       & Buziness Class        & Certificate\\
2010    & ITIL v.3      & IT Expert     & Certificate\\
2007    & SEP-EXP Managing stakeholder expectations     & RUSSEE/TEKAMA&        Certificate\\
2007    & SEP-REQD Requirements Development     & RUSSEE/TEKAMA&        Certificate\\
2006    & SEP-REQM Requirements and changes
in software development & RUSSEE/TEKAMA&        Certificate\\
2006    & SEP-PEP Software project estimation   & RUSSEE/TEKAMA & Certificate\\
2005    & PMPW02 Practical methods of effective
risk management, change management
and project team management.    & IT Expert/PM Expert&  Certificate\\
2005    & PMBS02 ANSI PMI PMBOK 3rd edition     & IT Expert/PM Expert&  Certificate\\
\end{longtable}
\fi

\noindent My Publications — \href{http://RaufAliev.ru/cv/rus/publications/}{www.RaufAliev.ru/cv/rus/publications} (rus) My talks — \href{http://raufaliev.ru/cv/eng/events/}{www.RaufAliev.ru/cv/eng/events/}



\end{document}             % End of document.

\begin{itemize}